quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Added Mapping the points to their corresponding hexagonal bins

@@

>>>>

The `compute_std_counts()` function calculates both the raw and standardized counts for each hexagon.

The function begins by grouping the data by `hexID` and counting the number of NLDR points falling within each bin. These raw counts are stored as `bin_counts`. To enable comparisons across bins with varying densities, the function then standardizes these counts by dividing each bin’s count by the maximum count across all bins. This yields a normalized metric, `std_counts`, ranging from 0 to 1.

@@

The `find_pts()` function extracts the list of data point identifiers (`ID`) assigned to each hexagon in the NLDR space.

The function first groups the input data by `hexID`, which represents the hexagon label associated with each point in the $2-\text{D}$ layout. Within each group, it collects the `ID`s into a list, resulting in a summary data frame where each row corresponds to a single hexagon. The resulting column, `pts_list`, contains all point identifiers associated with that hexagon.

### 2025-05-12 paper-quollr.tex
Added Mapping the points to their corresponding hexagonal bins

@@

>>>>

The \texttt{compute\_std\_counts()} function calculates both the raw and standardized counts for each hexagon.

The function begins by grouping the data by \texttt{hexID} and counting the number of NLDR points falling within each bin. These raw counts are stored as \texttt{bin\_counts}. To enable comparisons across bins with varying densities, the function then standardizes these counts by dividing each bin's count by the maximum count across all bins. This yields a normalized metric, \texttt{std\_counts}, ranging from 0 to 1.

@@

The \texttt{find\_pts()} function extracts the list of data point identifiers (\texttt{ID}) assigned to each hexagon in the NLDR space.

The function first groups the input data by \texttt{hexID}, which represents the hexagon label associated with each point in the \(2-\text{D}\) layout. Within each group, it collects the \texttt{ID}s into a list, resulting in a summary data frame where each row corresponds to a single hexagon. The resulting column, \texttt{pts\_list}, contains all point identifiers associated with that hexagon.
